Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-06-01 paper/sec-intro.tex
more work on text

The structure of this paper is the following.

>>>>

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the generation of the signal
and background Monte Carlo samples.
%
Then in Sect.~\ref{sec:analysis}
we describe our analysis strategy, and in particular
the classification of each individual event into
different categories according to the event topology.
%
The results for our traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance by means of multivariate techniques.
%
Finally in Sect.~\ref{sec:conclusions} we conclude and outline
possible future developements for Higgs pair production
in the $b\bar{b}b\bar{b}$ final state.
